Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Fix grammar and semantic

Unfortunately, the type system of Haskell does not always guarantee
correct semantics.
For example, it does not ensure that division by zero does not occur.
An other example is, that instances of {\tt Monoid} \emph{should} be
monoids in the mathematical sense, but the type system does not
enforce this.  It is the programmers responsibility to ensure that
instance definitions \emph{behave} as \emph{expected}.

Haskell programmers, however, are apt to rely on the type system too
much and tend not to write test code.  For example, Haskell
Platform 2011.4.0.0 contains 23 packages, not counting the 19 core
libraries that come with GHC.  Only 8 of them have a test suite, 5
provide example code, and 10 have neither tests nor examples.
A lack of tests is not only a quality and maintainability issue.  It
also is a lack of documentation.  Tests document how code is supposed
to be used, and tests document the behavior of code.

>>>>

Unfortunately, the type system of Haskell does not always guarantee
correct semantics.
For example, it does not ensure that division by zero does not occur.
An other example is, that instances of {\tt Monoid} \emph{should} be
monoids in the mathematical sense, but the type system does not
enforce this.  It is the programmers responsibility to ensure that
instance definitions \emph{behave} as \emph{expected}.  Hence
automated testing is useful.

However, some widely used Haskell libraries do not have automated
tests.  For example, the Haskell Platform 2011.4.0.0 contains 23
packages, not counting the 19 core libraries that come with GHC.  Only
8 of them have a test suite, 5 provide example code, and 10 have
neither tests nor examples.  A lack of tests is not only a quality and
maintainability issue.  It also is a lack of documentation.  Tests
document how code is supposed to be used, and tests document the
behavior of code.
